---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# parmsurvfit

The goal of parmsurvfit is to create functions that display output for Survival Analysis
that are easily available in Minitab, but much more difficult to obtain in R. All of the
functions in this package are assuming that the data follows a specified parametric distribution. 
Some examples of some of the items that are readily available in Minitab but not in R, that we 
attempted to easily recreate in R are as follows:  

* Computing survival probablities based on a specified parametric distribution  
* Displaying an estimated survival, hazard, or cumulative hazard curve based on a specified
parametric distribution (singular as well as by groups)  
* Estimating survival times based on a specified parametric distribution   
* Estimating parameters based on a specified parametric distribution    
* Estimating various statistics, including mean, median, standard deviation, and percentiles of
survival time based on a specified parametric distribution   
* Producing a qq-plot to examine distribution fit 
* Computing the Anderson-Darling test statistic as a measure of fit for a specified parametric
distribution

## Installation

You can install parmsurvfit from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("apjacobson/parmsurvfit")
```

## Examples

The following lines of code are examples of how to use the plotting functions in parmsurvfit:

```{r example}
library(survival)
data("rats")
plot_surv(rats, "weibull", time = "time", censor = "status")
plot_haz(rats, "weibull", time = "time", censor = "status")
plot_cumhaz(rats, "weibull", time = "time", censor = "status")

plot_density(rats, "weibull", time = "time", censor = "status")
plot_qqsurv(rats, "weibull", time = "time", censor = "status")
```

The following shows how to use other functions in parmsurvfit:

```{r example}
library(survival)
data("rats")
surv_summary(rats, "weibull", censor = "status")
surv_prob(rats, "weibull", 80, censor = "status")
compute_AD(rats, "weibull", censor = "status")
```

