---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/"
)
```

# parmsurvfit

This package executes simple parametic models for right-censored survival data.  Functionality emulates capabilities in Minitab, including fitting right-censored data, assessing fit, plotting survival functions, and summary statistics and probabilities.


## Installation

You can install parmsurvfit from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("apjacobson/parmsurvfit")
```

## Examples

```{r}
library(parmsurvfit)
```

Fitting data and assessing fit:

```{r}
fit_data(data = firstdrink, dist = "weibull", time = "age")
plot_density(data = firstdrink, dist = "weibull", time = "age")
plot_ppsurv(data = firstdrink, dist = "weibull", time = "age")
compute_AD(data = firstdrink, dist = "weibull", time = "age")
```

Survival functions:

```{r}
plot_surv(data = firstdrink, dist = "weibull", time = "age")
plot_haz(data = firstdrink, dist = "weibull", time = "age")
plot_cumhaz(data = firstdrink, dist = "weibull", time = "age")
```

Summary statistics and probabilities:

```{r}
surv_prob(data = firstdrink, dist = "weibull", x = 30, lower.tail = F, time = "age")
surv_summary(data = firstdrink, dist = "weibull", time = "age")
```
