---
title: "Guide to Using parmsurvfit"
author: "Ashley Jacobson & Victor Wilson"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Guide to using parmsurvfit}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  \usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction
 
The motivation for this package is to create functions that display output for Survival Analysis
that are easily available in Minitab, but much more difficult to obtain in R. All of the
functions in this package are assuming that the data follows a specified parametric distribution. 
Some examples of some of the items that are readily available in Minitab but not in R, that we 
attempted to easily recreate in R are as follows:  

* Computing survival probablities based on a specified parametric distribution  
* Displaying an estimated survival, hazard, or cumulative hazard curve based on a specified
parametric distribution (singular as well as by groups)  
* Estimating survival times based on a specified parametric distribution   
* Estimating parameters based on a specified parametric distribution    
* Estimating various statistics, including mean, median, standard deviation, and percentiles of
survival time based on a specified parametric distribution   
* Producing a qq-plot to examine distribution fit 
* Computing the Anderson-Darling test statistic as a measure of fit for a specified parametric
distribution

# Fitting Right Censored Survival Data

In order for any of the functions in this package to work, the dataset must be formatted
correctly, using the 'fit_data' function, which fits right censored data to a distribution
using maximum likelihood estimates. This function is very similar to the 'fitdistcens' function
which is already available in R via the fitdistrplus package, but is specifically set up to deal 
with datasets that are designed for survival analysis.

## Example

```{r}
library(parmsurvfit)
library(survival)
data("rats")
fit_data(rats, "logis", "time", "status")
```

# Plotting Survival Curves

The 'plot_surv' function plots the survival curve of right censored data, once it has been
formatted using the fit_data function, given that it follows a specified parametric
distribution. Plotted on the x-axis is time after start of observation, and plotted
on the y-axis is proportion of subjects surviving.

## Example

```{r}
library(survival) 
data("rats")
plot_surv(rats, "lnorm", time = "time", censor = "status")
```

As seen in this survival curve, roughly 40% of rats are estimated to survive beyond time t = 200. 

# Plotting Hazard Curves

The 'plot_haz' function plots the hazard curve of right censored data, given that it follows 
a specified parametric distribution. The hazard displays the conditional risk that a subject 
will experience the event of interest in the next instant of time, given that the subject has 
survived beyond a certain amount of time.
  
## Example

```{r}
library(survival)
data("rats")
plot_haz(rats, "weibull", time="time", censor="status")
```

# Plotting Cumulative Hazard Curves

The 'plot_cumhaz' funtion plots the cumulative hazard curve of right censored data, given that
it follows a specified parametric distribution. It is important to note that the cumulative
hazard function is neither a probability nor a rate, it is merely an accumlation of hazard
rates over time.
  
## Example

```{r}
library(survival)
data("rats")
plot_cumhaz(rats, "weibull", time="time", censor="status")
```

# Computing Survival Probabilities

This function computes survival probabilites, given that the data follows a specified
parametric distribution. The output in this function represents the estimated probability that 
a subject does not experience the event of interest beyond a specified time t. 
 
## Example

```{r}
library(survival)
data("rats")
surv_prob(rats, "lnorm", 110, time = "time", censor = "status")
```

Here we see that using the rats dataset found in the survival package, assuming that the data
follows a log-normal distribution, the probability that a rat survives beyond 110 days is 
roughly 0.8. 
 
# Computing Summary Statistics 

Another form of output that is easily computed in Minitab but not in R are various summary
statistics based on a specified parametric distribution. We developed the 'surv_summary' function
to combat this. This function estimates various statistics, including mean, median, standard
deviation, and percentiles of survival time given that the data follows a specified parametric
distribution.

## Example

```{r}
library(survival)
data("rats")
surv_summary(rats, "lnorm", time = "time", censor = "status")
```